13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2018-04-13 rules/rules18.tex
Minor

\begin{description}
\item[April~8] Deadline for new benchmark contributions.
\item[May~15] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~27] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~10] Deadline for final versions of solvers, including
  system descriptions.
\item[\rem{June~20 TODO update}] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~12/13] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

Within each track there are multiple divisions, where each division
uses benchmarks from a specific SMT-LIB logic (or group of logics).
We will recognize winners as measured by number of benchmarks solved;
we will also recognize solvers based on additional criteria.
\rem{Aina: Is this up to date? We do use weighting to determine a score that
determines the winner, right? So, it is actually not the number of solved
benchmarks that determines the winner.}

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Aaron Stump, and Tjark Weber.}
describes the rules and competition procedures for SMT-COMP~2018.  The
principal changes from the previous competition rules are the
following:
\rem{Aina: All of this bullets are not new in 2018 anymore, maybe move them
elsewhere? This information should not be lost.}
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
  language.  \emph{Rationale:} This is the latest version of the
  SMT-LIB language.  It is largely backwards-compatible with earlier
  versions (in particular~2.0 and~2.5).
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, or underspecified floating-point functions, such as
  \texttt{fp.min}, will be eligible for the competition again.
  \emph{Rationale:} A conclusion on the semantics of these functions
  has finally been reached, and the status of affected SMT-LIB
  benchmarks has been updated accordingly.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item In the competition-wide scoring, the (per-division) penalty for
  erroneous results is changed from the number of errors to a fixed
  constant (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in the division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition will feature experimental divisions for
  benchmarks that use algebraic datatypes.  \emph{Rationale:}
  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
  which is expected to become official in the near future, and are
  already supported by some solvers.  Benchmarks that use datatypes
  have recently been added to SMT-LIB.
\end{itemize}
\rem{Aina: Are we going to introduce an experimental strings divisions?}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \rem{TODO, this is still the old link}
  \url{https://goo.gl/forms/HL6rbOywqW4sFo1D2}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

\rem{Aina: Why are there no restrictions as to who can submit which solver?
Shouldn't we maybe introduce the requirement that only authors can submit
solvers? Else someone could, e.g., submit CVC4 or Z3 as their solver.}

\header{System description.}
%
As part of a submission, SMT-COMP entrants are encouraged to provide a
short (1--2 pages) description of the system.
\rem{Aina: I would actually make the submission of the system description a
requirement, if possible. I would also require that if entrants are based
on an already existing solver, this must be mentioned in the system description
and appropriate acknowledgement is due, same as with wrapper tools.}
This should include a
list of all authors of the system, their present institutional
affiliations, and any appropriate acknowledgements.  The programming
language(s) and basic SMT solving approach employed should be
described (e.g., lazy integration of a Nelson-Oppen combination with
SAT, translation to SAT, etc.).  System descriptions are encouraged to
include a URL for a web site for the submitted tool.  System
descriptions may be submitted after the solver deadline, but to be
useful should be sent to the organizers before the competition ends.
We intend to make system descriptions publicly available.

@@

\header{Wrapper tools.}
%
A \emph{wrapper tool} is defined as any solver which calls one or more
SMT solvers not written by the author of the wrapper tool.  The other
solvers are called the \emph{wrapped} solvers.  A wrapper tool must
explicitly acknowledge any solvers that it wraps.  Its system
description should make clear the technical innovations by which the
wrapper tool expects to improve on the wrapped solvers.
\rem{Aina: Again, I'd like to make the submission of system descriptions
mandatory. SAT competition does that as well, btw.}

@@

The time limit~$T$ is yet to be determined, but it is anticipated to
be at most 40~minutes of wall-clock time per solver/benchmark
pair.\footnote{The time limit may be adjusted once we know the number
  of competition entrants and eligible benchmarks.  Because of the
  inclusion of benchmarks with unknown status, the time limit may be
  lower than in previous years.}  Solvers that take more than this
time limit will be killed.  Solvers are allowed to spawn other
processes; these will be killed at approximately the same time as the
first started process.

@@

In order to perform this unsatisfiability check, the organizers will
use a selection of SMT solvers that participate in the main track
of this competition. For each division, the organizers will
use only solvers that have been sound (i.e., not
produced any erroneous result) in test runs of the
main track for this division.
The unsatisfiability of a produced unsatisfiable core is
refuted if the number of checking solvers whose result is \texttt{sat}
exceeds the number of checking solvers whose result is \texttt{unsat}.
The time limit for checking unsatisfiable
cores is yet to be determined, but is anticipated to be around 5
minutes of wall-clock time per solver.

@@

\header{Main track: removal of disagreements.}
%
Before division scores are computed for the main track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its raw score (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores.
\rem{Aina: I strongly suggest that we make disagreements visible.
I would add a table to the bottom of the division results page, where
we list the benchmarks we removed due to disagreements and which results
which solvers reported. Silently dropping benchmarks on which solvers
disagree is potentially unfair and dangerous, since people who want to use
a solver, tend to only
look at the SMT-COMP results and pick a solver based on this results.
They will certainly not go through the competition results on StarExec,
in particular since this is quite tedious.
For users it is interesting (and might be actually crucial) to know
if a solver disagreed with other solvers.
The same is true for solver developers, since they certainly want to know
if their solver disagreed with other solvers on a certain benchmark.
They usually run preliminary tests with existing solvers beforehand,
but not all solvers are available in the newest version.
Not to mention new solvers.}

@@

\rem{Aina: Depending on the number of medals we get from FLOC we should
decide on how to categorize for prizes. Some ideas:
\begin{itemize}
  \item Competition-wide, main track, best solver
  \item Quantified divisions, best solver
  \item Either QF\_BV best solver, or QF\_BV + QF\_ABV + QF\_AUFBV + QF\_UFBV
  \item Comptetition-wide, application track, best solver
  \item Comptetition-wide, unsat-core track, best solver
  \item Best newcomer
\end{itemize}
Floating-point is currently only officially supported by Z3,
inofficially also by CVC4, if we expect more than 2 entrants, then FP logics
would also be a candidate.
}

>>>>

\begin{description}
\item[April~8] Deadline for new benchmark contributions.
\item[May~15] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~27] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~10] Deadline for final versions of solvers, including
  system descriptions.
\item[June~11] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~12/13] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

Within each track there are multiple divisions, where each division
uses benchmarks from a specific SMT-LIB logic (or group of logics).
We will recognize winners as measured by number of benchmarks solved
(taking into account the weighting detailed in
Section~\ref{sec:scoring}); we will also recognize solvers based on
additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following: \rem{Aina: All of this bullets are not new in
  2018 anymore, maybe move them elsewhere? This information should not
  be lost.}
\begin{itemize}
\item Submission of accompanying information for solvers is via a web
  form (rather than by email to the organizers).  \emph{Rationale:}
  Email submissions were often incomplete, leading to ambiguity and
  further inquiries.  The form provides a more structured way of
  submitting information.
\item Benchmarks will use (a subset of) version~2.6 of the SMT-LIB
  language.  \emph{Rationale:} This is the latest version of the
  SMT-LIB language.  It is largely backwards-compatible with earlier
  versions (in particular~2.0 and~2.5).
\item Benchmarks that use partial bit-vector functions, such as
  \texttt{bvudiv}, or underspecified floating-point functions, such as
  \texttt{fp.min}, will be eligible for the competition again.
  \emph{Rationale:} A conclusion on the semantics of these functions
  has finally been reached, and the status of affected SMT-LIB
  benchmarks has been updated accordingly.
\item Benchmarks with unknown status will be eligible for the
  competition's main track.  In 2016, solver performance on benchmarks
  with unknown status was evaluated but reported separately; in 2017,
  it will directly affect the competition results.  \emph{Rationale:}
  Using only benchmarks with known status (i.e., benchmarks that have
  been solved before) to determine the competition results unjustly
  favors imitation of existing solvers over true innovation.
\item In the competition-wide scoring, the (per-division) penalty for
  erroneous results is changed from the number of errors to a fixed
  constant (multiplied by the weight of the respective division).
  \emph{Rationale:} The weight already takes the number of benchmarks
  in the division into account; multiplying it by the number of errors
  overemphasizes large divisions.
\item The unsat-core track, which was re-introduced in 2016, is no
  longer experimental.  Its divisions will be considered competitive
  if the necessary requirements (see Section~\ref{sec:scoring}) are
  met.  \emph{Rationale:} Rules and tool support for the unsat-core
  track proved sufficiently stable in 2016.
\item The competition will feature experimental divisions for
  benchmarks that use algebraic datatypes.  \emph{Rationale:}
  Algebraic datatypes are specified in the draft SMT-LIB~2.6 standard,
  which is expected to become official in the near future, and are
  already supported by some solvers.  Benchmarks that use datatypes
  have recently been added to SMT-LIB.
\end{itemize}
\rem{Aina: Are we going to introduce an experimental strings divisions?}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \rem{TODO, this is still the old link: https://goo.gl/forms/HL6rbOywqW4sFo1D2}
  {\tt TBA}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

\header{System description.}
%
As part of a submission, SMT-COMP entrants are strongly encouraged to
provide a short (1--2 pages) description of the system.  This should
include a list of all authors of the system, their present
institutional affiliations, and any appropriate acknowledgements.  The
programming language(s) and basic SMT solving approach employed should
be described (e.g., lazy integration of a Nelson-Oppen combination
with SAT, translation to SAT, etc.).  System descriptions should also
include a URL for a web site for the submitted tool.  System
descriptions may be submitted after the solver deadline, but to be
useful should be sent to the organizers before the competition ends.
We intend to make system descriptions publicly available.

@@

\header{Wrapper tools.}
%
A \emph{wrapper tool} is defined as any solver which calls (or is in
some other way based on) one or more SMT solvers not written by the
author of the wrapper tool.  The other solvers are called the
\emph{wrapped} solvers.  A wrapper tool must explicitly acknowledge
any solvers that it wraps.  Its system description should make clear
the technical innovations by which the wrapper tool expects to improve
on the wrapped solvers.

@@

The time limit~$T$ is yet to be determined, but it is anticipated to
be at most 20~minutes of wall-clock time per solver/benchmark
pair.\footnote{The time limit may be adjusted once we know the number
  of competition entrants and eligible benchmarks.}  Solvers that take
more than this time limit will be killed.  Solvers are allowed to
spawn other processes; these will be killed at approximately the same
time as the first started process.

@@

In order to perform this unsatisfiability check, the organizers will
use a selection of SMT solvers that participate in the main track of
this competition.  For each division, the organizers will use only
solvers that have been sound (i.e., not produced any erroneous result)
in the main track for this division.  The unsatisfiability of a
produced unsatisfiable core is refuted if the number of checking
solvers whose result is \texttt{sat} exceeds the number of checking
solvers whose result is \texttt{unsat}.  The time limit for checking
unsatisfiable cores is yet to be determined, but is anticipated to be
around 5 minutes of wall-clock time per solver.

@@

\header{Main track: removal of disagreements.}
%
Before division scores are computed for the main track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its raw score (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores (but the organizers may report disagreements for informational
purposes).
\rem{Aina: I strongly suggest that we make disagreements visible.  I
  would add a table to the bottom of the division results page, where
  we list the benchmarks we removed due to disagreements and which
  results which solvers reported. Silently dropping benchmarks on
  which solvers disagree is potentially unfair and dangerous, since
  people who want to use a solver, tend to only look at the SMT-COMP
  results and pick a solver based on this results.  They will
  certainly not go through the competition results on StarExec, in
  particular since this is quite tedious.  For users it is interesting
  (and might be actually crucial) to know if a solver disagreed with
  other solvers.  The same is true for solver developers, since they
  certainly want to know if their solver disagreed with other solvers
  on a certain benchmark.  They usually run preliminary tests with
  existing solvers beforehand, but not all solvers are available in
  the newest version.  Not to mention new solvers.}

@@

\rem{Aina: Depending on the number of medals we get from FLOC we should
decide on how to categorize for prizes. Some ideas:
\begin{itemize}
  \item Competition-wide, main track, best solver
  \item Quantified divisions, best solver
  \item Either QF\_BV best solver, or QF\_BV + QF\_ABV + QF\_AUFBV + QF\_UFBV
  \item Competition-wide, application track, best solver
  \item Competition-wide, unsat-core track, best solver
  \item Best newcomer
\end{itemize}
Floating-point is currently only officially supported by Z3,
inofficially also by CVC4, if we expect more than 2 entrants, then FP logics
would also be a candidate.
}
